### 2012-11-15 ASA2013/asa2013.tex
la2pdf commit - 2012:11:15	17:14:28	(Thu15.Nov)

For systems with less than 32 channels, we suggest arithmetic optimizations for the estimation step, and show how a GPU can be used to yield processing rates of more than 1\,Mpx/s. When the system exceeds this size, we show that frequency domain processing can be employed, which allows a comparable performance to be maintained, at a neglible reduction in image quality. These GPU implementations consistently reduced the runtime by 2-3 orders of magnitude compared to our reference C and Matlab implementations.

Should this this still be insufficient, we suggest having a look that the LCA beamformer. It does not compute a weightset, but merely computes the beamformer output for each of a each predefined set of weights, and selects the one that best fulfills the MVDR criteria. The images it produces are comparable to the MVDR, without the development cost or complexity of the MVDR, and it is perfectly suited for a GPU.

>>>>

For systems with relatively few channels, we suggest arithmetic optimizations for the estimation step, and show how a GPU can be used to yield processing rates of more than 1\,Mpx/s. For larger systems  we show that frequency domain processing is preferable. This allows a comparable performance to be maintained at a negligible reduction in image quality. These GPU implementations consistently reduced the runtime by 2-3 orders of magnitude compared to our reference C and Matlab implementations.

For even larger systems we suggest employing the LCA beamformer. It does not compute a weightset, but merely computes the beamformer output for each of a predefined set of weights, and selects the one that best fulfils the MVDR criterion. The LCA creates images with a quality comparable to MVDR, and it is perfectly suited for a GPU.
